Representation Project

### 2025-01-25 manuscript/manuscript.qmd
manuscript updates; git cache reset

---
title: "Planning to Save Energy: How Information Format Affects Accuracy"
aliases:
  - /manuscript.html
format-links:   
    - text: HTML
      href: manuscript.html
      icon: file-minus
    - text: HTML (with code)
      href: manuscript-code.html
      icon: file-plus
    - format: hikmah-manuscript-pdf
      text: PDF version
      icon: file-pdf
    - docx
    - gfm
date: 2025-01-12
abstract: |
    Effective communication of energy consumption information is crucial for promoting residential energy conservation. This study investigates how different numerical representations of energy reduction goals influence consumers' ability to create accurate conservation plans. Across two experiments, we examined the impact of presenting energy information in kilowatt-hours (kWh), percentages, or U.S. dollars (USD) on planning accuracy. Participants completed a simulated household planning task in which they allocated energy usage across multiple appliances, with the goal presented in either kilowatt-hours (kWh), percentages, or monetary costs. Results across both experiments showed that presenting reduction goals in absolute units (kWh) led to significantly greater accuracy compared to percentage-based or monetary formats. Furthermore, we found that higher energy literacy was associated with more accurate planning. These findings demonstrate that absolute units (kWh) are more effective for communicating energy-saving goals, and highlight the potential value of educational interventions to improve consumer energy literacy.
---

@@

### Literature Review

Energy insecurity has emerged as a critical public health concern, especially among low-income households, who frequently face difficult choices between paying energy bills and meeting other essential needs [@bednarRecognitionResponseEnergy2020; @memmottSociodemographicDisparitiesEnergy2021]. Such households often experience unsafe coping strategies (e.g., foregoing heating during winter months), which disproportionately affect racial and ethnic minorities and heighten risks of utility disconnection  [@memmottSociodemographicDisparitiesEnergy2021]. Moreover, residential energy use contributes to climate change, intensifying the urgency for sustainable solutions [@farghaliStrategiesEnergyContext2023].  Promoting behavior change to reduce energy consumption is crucial. However, the success of such interventions may hinge on how effectively energy information is communicated, with format and presentation context significantly influencing understanding and action [@canfieldPerceptionsElectricityuseCommunications2017; @fischerFeedbackHouseholdElectricity2008]. Consequently, a pressing challenge lies in designing communication strategies that effectively convey energy data and motivate practical conservation decisions

The way numerical information is presented can significantly affect how individuals process and use that information. Of particular relevance are reference class effects, which occur when numerical statements are presented without a clear or intuitive basis for comparison, making it difficult to infer meaningful quantities[@gigerenzerSimpleToolsUnderstanding2003; @reimerNumericCommunicationRisk2015]. A substantial body of evidence suggests that presenting data in terms of absolute counts or frequencies, as opposed to probabilities or percentages, can promote more accurate comprehension and facilitate decision making. However, it's important to note that even intuitive formats can pose challenges. For instance, @weberWhyCanOnly2018 found that individuals often struggle with reasoning tasks presented in natural frequencies because they inadvertently revert to more complex probabilistic thinking.

@@

Although many individuals express a desire to conserve energy, research consistently shows that abstract goals (e.g., “reduce overall usage by 15%”) often fail to translate into effective behavior change unless accompanied by specific, actionable steps [@abrahamseReviewInterventionStudies2005; @nematiImpactInformationbasedInterventions2020]. For instance, @abrahamseReviewInterventionStudies2005 demonstrated that merely providing general information about energy savings rarely alters consumption patterns unless consumers also receive concrete instructions or tailored feedback. Similarly, @tonkeProvidingProceduralKnowledge2024 reported that sending households brief but precise text messages outlining how to reduce water use (e.g., limiting irrigation times, adjusting washing machine settings) yielded meaningful decreases in consumption, underscoring the importance of procedural knowledge—namely, knowing how to operationalize a goal rather than simply why it is desirable. In the context of energy conservation, this implies that interventions should not only highlight potential reductions (such as a 15% target) but also guide residents in allocating those reductions across specific appliances or behaviors [@attariPublicPerceptionsEnergy2010]. Additionally, meta-analytic findings suggest that people respond more robustly to household-level feedback that situates their usage within a personalized framework, thereby reducing the cognitive burden of determining next steps [@nematiImpactInformationbasedInterventions2020].

>>>>

---
title: "Planning to Save Energy: How Information Format Affects Accuracy"
aliases:
  - /manuscript.html
format-links:   
    - text: HTML
      href: manuscript.html
      icon: file-minus
    - text: HTML (with code)
      href: manuscript-code.html
      icon: file-plus
    - format: hikmah-manuscript-pdf
      text: PDF version
      icon: file-pdf
    - text: docx
      href: rs_manuscript_apa.docx
    - gfm
date: 2025-01-12
abstract: "Effective communication of energy consumption information is crucial for promoting residential energy conservation. This study investigates how different numerical representations of energy reduction goals influence consumers' ability to create accurate conservation plans. Across two experiments, we examined the impact of presenting energy information in kilowatt-hours (kWh), percentages, or U.S. dollars (USD) on planning accuracy. Participants completed a simulated household planning task in which they allocated energy usage across multiple appliances, with the goal presented in either kilowatt-hours (kWh), percentages, or monetary costs. Results across both experiments showed that presenting reduction goals in absolute units (kWh) led to significantly greater accuracy compared to percentage-based or monetary formats. Furthermore, we found that higher energy literacy was associated with more accurate planning. These findings demonstrate that absolute units (kWh) are more effective for communicating energy-saving goals, and highlight the potential value of educational interventions to improve consumer energy literacy."
---

@@

Energy insecurity has emerged as a critical public health concern, especially among low-income households, who frequently face difficult choices between paying energy bills and meeting other essential needs [@bednarRecognitionResponseEnergy2020; @memmottSociodemographicDisparitiesEnergy2021]. Such households often experience unsafe coping strategies (e.g., foregoing heating during winter months), which disproportionately affect racial and ethnic minorities and heighten risks of utility disconnection  [@memmottSociodemographicDisparitiesEnergy2021]. Moreover, residential energy use contributes to climate change, intensifying the urgency for sustainable solutions [@farghaliStrategiesEnergyContext2023].

Given the relevance of promoting behavior change to reduce energy consumption, several strands of research have aimed to identify factors that affect energy behaviors and interventions that effectively reduce energy consumption. Interventions often focus on X, Y, Z. For example, …

However, the success of such interventions may hinge on how effectively energy information is communicated, with format and presentation context significantly influencing understanding and action [@canfieldPerceptionsElectricityuseCommunications2017; @fischerFeedbackHouseholdElectricity2008]. Consequently, a pressing challenge lies in designing communication strategies that effectively convey energy data and motivate practical conservation decisions. We set out to explore if consumers are able to develop plans that would help meet certain energy consumption goals.

### Representation Formats

Receiving feedback about one’s energy use is an important step in identifying potential actions to reduce energy consumption. However, it is crucial to understand how consumers use the information that is given with their energy bill and whether consumers are able to translate a energy saving goal into an action plan.

Building on the study of Canfield et al. (2017), we aimed to test xxx.

Although many individuals express a desire to conserve energy, research consistently shows that abstract goals (e.g., “reduce overall usage by 15%”) often fail to translate into effective behavior change unless accompanied by specific, actionable steps [@abrahamseReviewInterventionStudies2005; @nematiImpactInformationbasedInterventions2020]. For instance, @abrahamseReviewInterventionStudies2005 demonstrated that merely providing general information about energy savings rarely alters consumption patterns unless consumers also receive concrete instructions or tailored feedback.

Similarly, @tonkeProvidingProceduralKnowledge2024 rreported that sending households brief but precise text messages outlining how to reduce water use (e.g., limiting irrigation times, adjusting washing machine settings) yielded meaningful decreases in consumption, underscoring the importance of procedural knowledge—namely, knowing how to operationalize a goal rather than simply why it is desirable. In the context of energy conservation, this implies that interventions should not only highlight potential reductions (such as a 15% target) but also guide residents in allocating those reductions across specific appliances or behaviors [@attariPublicPerceptionsEnergy2010]. Additionally, meta-analytic findings suggest that people respond more robustly to household-level feedback that situates their usage within a personalized framework, thereby reducing the cognitive burden of determining next steps [@nematiImpactInformationbasedInterventions2020].

The way numerical information is presented can significantly affect how individuals process and use that information. Of particular relevance are reference class effects, which occur when numerical statements are presented without a clear or intuitive basis for comparison, making it difficult to infer meaningful quantities[@gigerenzerSimpleToolsUnderstanding2003; @reimerNumericCommunicationRisk2015]. A substantial body of evidence suggests that presenting data in terms of absolute counts or frequencies, as opposed to probabilities or percentages, can promote more accurate comprehension and facilitate decision making. However, it is important to note that even intuitive formats can pose challenges. For instance, @weberWhyCanOnly2018 found that individuals often struggle with reasoning tasks presented in natural frequencies because they inadvertently revert to more complex probabilistic thinking.

@@

### Overview of Current Research

### 2025-01-25 nb/study2.qmd
manuscript updates; git cache reset

---
title: "Study 2 Analysis"
lightbox: true
toc: false
date: today
execute:
  #echo: false
  warning: false
cache: true
format:
  html:

    grid:
      sidebar-width: 220px
      body-width: 1200px
      margin-width: 170px
      gutter-width: 1.0rem
  hugo-md:
    include: true
    html-math-method: mathjax
    output-file: s2_hugo.md
  gfm:
    echo: true
    output-file: s2_gfm.md
---

>>>>

---
title: "Study 2 Analysis"
lightbox: true
toc: false
date: today
execute:
  #echo: false
  warning: false
cache: true
format:
  html: 
    grid:
      sidebar-width: 220px
      body-width: 1200px
      margin-width: 170px
      gutter-width: 1.0rem
  hugo-md:
    include: true
    html-math-method: mathjax
    output-file: s2_hugo.md
  gfm:
    echo: true
    output-file: s2_gfm.md
---

### 2025-01-25 paper.qmd
Analysis on energy literacy
manuscript updates; git cache reset

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.docx">
  <i class="fa-solid fa-file-word"></i>&ensp;docx <small>(download)</small>
  </a>

@@

<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:75%;width:95%;border:2px solid #ccc;" height="75%" width="95%" name="manuscript"></iframe>
```

>>>>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/rs_manuscript_apa.docx">
  <i class="fa-solid fa-file-word"></i>&ensp;docx <small>(download)</small>
  </a>

@@

<iframe src="/manuscript/output/manuscript.html" frameborder=".1" style="overflow:hidden;height:75%;width:95%;border:2px solid #ccc;" height="75%" width="98%" name="manuscript"></iframe>
```
